When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-02-22 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
wrote results for H2a

The rmANOVA showed a significant difference between the SVs across *n*-back levels (`r apa_print(hypothesis2a_rmanova)$full_result$level`, `r apa_print(hypothesis2a_BF)$statistic`).

>>>>

The rmANOVA showed a significant difference between the SVs across *n*-back levels (`r apa_print(hypothesis2a_rmanova)$full_result$level`, `r apa_print(hypothesis2a_BF)$statistic`).
All four pre-defined contrasts reached significance (Table\ \@ref(tab:H2a-contrasts)), so a purely linear contrast can be rejected.

```{r H2a-contrasts, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis2a_contrasts,
  caption = "Contrasts for the rmANOVA comparing the subjective values between *n*-back levels",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

The declining logistic contrast had the highest effect estimate (`r apa_print(emmeans::contrast(hypothesis2a_emm, method = list("decl_log" =c(3,2,-2,-3))))$full_result`), suggesting a shallow decline of SVs between 1- and 2-back, and 3- and 4-back, respectively, and a steeper decline of SVs between 2- and 3-back.
